Object naming is context-dependent - A case study on testing linguistic hypotheses on real-world image corpora

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex

>>>>

\begin{table}
\centering
\setlength{\tabcolsep}{2pt}
\begin{tiny}
\begin{tabular}{rrl|rrl}
\toprule
 spec. &  rel.freq. &                          top 5 names & spec. &  rel.freq. &                          top 5 names \\
\midrule
           2 &   $<$ 0.01 &       \tiny                  thing,things & 10 &   0.05 &   elephant,couch,truck,vase,suitcase \\
           3 &   $<$ 0.01 &    object,group,set,substance,objects & 11 &   $<$ 0.01 &    motorcycle,clock,mom,dad,scissors \\
           4 &   0.14 &           man,person,piece,head,part & 12 &   $<$ 0.01 &  oven,airplane,suv,taxi,refrigerator  \\
           5 &   0.10 &       player,glass,baby,front,corner & 13 &   $<$ 0.01 &    laptop,fridge,canoe,orioles,pigeon \\
           6 &   0.21 &              woman,girl,kid,boy,bowl & 14 &   $<$ 0.01 &   panda,freezer,penguin,rooster,rhino \\
           7 &   0.25 &            guy,right,chair,lady,bear & 15 &   0.03 &    zebra,giraffe,zebras,giraffes,deer \\
           8 &   0.11 &           horse,bus,cow,pizza,batter & 16 &  $ <$ 0.01 &       bison,mooses,orang,elks,sambar \\
           9 &   0.09 &         shirt,car,bike,donut,catcher & 17 &   $<$ 0.01 &           ox,cattle,gnu,mustang,orca \\          
\bottomrule
\end{tabular}\caption{Levels of specificity for naming choices in RefCOCO: for each level (distance between name and WordNet root), relative frequency and 5 most frequent names are shown}
\label{tab:specnames}
\end{tiny}
\vspace{-1cm}
\label{tab:specnames}
\end{table}
\vspace{-0.6cm}
